
Rudolph C. 2003. Security and the political
economy of international migration. Am.
Polit. Sci. Rev. 97(4):603–20

Teitelbaum MS. 1984. Immigration, refugees,
and foreign policy. Int. Organ. 38(3):429–50

Foreign-Born Voting Behavior in Local Elections
Evidence From New Immigrant Destinations
http://apr.sagepub.com/content/43/1/27.abstract

From Coverage to Action
The Immigration Debate and Its Effects on Participation
Merolla
Adrian D. Pantoja2
Ivy A. M. Cargile1
Juana Mora1
http://prq.sagepub.com/content/66/2/322.abstract

Anti-Immigrant Prejudice in Europe: Contact, Threat Perception, and Preferences for the Exclusion of Migrants*
Lauren M. McLaren⇓

National Security and Immigration: Policy Development in the United States ...
By Christopher Rudolph
2006

Immigration Policy and Security: U.S., European, and Commonwealth Perspectives
edited by Terri Givens, Associate Professor Department of Government Gary P Freeman, Gary P. Freeman, David L. Leal
2009

Public Policy and the New European Agendas
By F. Carr

Tumlin, K.C. (2004). Suspect first: How terrorism policy is reshaping immigration policy. California law review, 92(4). Pp. 1173-1239.

Miriam Wells, “The Grassroots Reconfiguration of U.S. Immigration Policy,” International Migration Review, Vol. 38, No. 4
Tichenor, D. (2002). Dividing Lines: The Politics of Immigration Control in America, Princeton: Princeton University Press

Zolberg, Aristide. 2000. “Matters of State:  Theorizing Immigration Policy.”  The Handbook of International Migration.

Tichenor, Daniel J. 2002. Dividing Lines:  The Politics of Immigration Control in America

[14] A. L. Esp´ındola, J. J. Silveira, and T. J. P. Penna, “A Harris-Todaroagent-based model to rural-urban migration,” Brazilian Journal ofPhysics, vol. 36, no. 3a, Sep. 2006.

[15] S. Sun and S. M. Manson, “An Agent-based Model of Housing Searchand Intraurban Migration in the Twin Cities of Minnesota,” TransportEconomics, 2010.	

Bijwaard and van Doeselaar, 2012; 
Bijwaard et al., 2013
Bijwaard and Qi Wang, 2013
Gampe et al., 2009